Analysis-ready VCF at Biobank scale using Zarr

### 2025-03-05 paper.tex
We current support cloud stores
Add Data Availbility section

\subsection{Interoperability: vcztools}
To provide compatibility with existing workflows we have
developed the \texttt{vcztools} command line utility which
implements a subset of \texttt{bcftools} functionality.
Vcztools is intended to be a drop-in replacement for \texttt{bcftools},
providing an evolutionary path for VCF Zarr adoption,
with compatibility being a core objective.
Vcztools currently supports Zarr stored in the local file system
and Zip archives, and support for major cloud stores will be added in the near future. 
Thus, users can convert their VCF data to Zarr using \texttt{bio2zarr},
store it in a local file system, Zip file or cloud store as desired
and then access this data source within existing processing pipelines,
essentially replacing \texttt{bcftools view <vcf file>} with
\texttt{vcztools view <Zarr URL>}.
This allows established analysis workflows to coexist with new Zarr-native
approaches, working from the same primary data.

@@

>>>>

\subsection{Interoperability: vcztools}
To provide compatibility with existing workflows we have
developed the \texttt{vcztools} command line utility which
implements a subset of \texttt{bcftools} functionality.
Vcztools is intended to be a drop-in replacement for \texttt{bcftools},
providing an evolutionary path for VCF Zarr adoption,
with compatibility being a core objective.
Vcztools currently supports Zarr stored in the local file system,
Zip archives, and major cloud stores.
Thus, users can convert their VCF data to Zarr using \texttt{bio2zarr},
store it in a local file system, Zip file or cloud store as desired
and then access this data source within existing processing pipelines,
essentially replacing \texttt{bcftools view <vcf file>} with
\texttt{vcztools view <Zarr URL>}.
This allows established analysis workflows to coexist with new Zarr-native
approaches, working from the same primary data.

@@

\section{Data availability}

No novel datasets were generated for this work.
